Astr 513: Final Project

### 2016-04-30 Final_Project/ms.tex
Updated Section 1 and added some new references

\section{Type Ia Supernovae}
\label{sec:SNIa}
\TM{TODO: Complete this section.}

@@

\citet{betoule2014} define their ``joint light-curve analysis'' (JLA) 
sample, a total of 740 type Ia supernovae (SNe Ia) 
%If we define the abbreviations elsewhere, this can change -- ELW
compiled from a combination of data from the Sloan Digital Sky 
Survey (SDSS), the Supernova Legacy Survey (SNLS), the Hubble Space 
Telescope (HST), and several other experiments. The 613 SDSS \snea{} 
come from the SDSS supernova survey (SDSS-SNS) of SDSS-II \citep{sako2014} 
with redshifts of $0.05 < z < 0.4$, and 374 of them are selected from those 
that were confirmed in the spectroscopic follow-up. The rest of the 
\sne{} come from the compilation by \citet{conley2011}, which includes 
242 spectroscopically confirmed \snea{} from SNLS at redshifts $0.2 < z < 1$, 
14 \snea{} from HST at very high redshifts of $0.7 < z < 1.4$, and 123 
low redshift ($z < 0.08$) from a variety of sources. We made use of the 
publicly available distance moduli, redshifts, and covariance 
matrix provided by \citet{betoule2014}\footnote{Data is available 
for download via \url{http://cdsweb.u-strasbrg.fr/cgi-bin/qcat?J/A+A/568/A22}}. 
We note that the distance moduli are binned, so that they are only computed and 
given on a grid of redshifts. The distance modulus can then be well 
approximated by a piecewise linear function of $\log(z)$ that is given 
in a single redshift bin $z_b \le z < z_{b+1}$ as 
\citep[see][Appendix E.1]{betoule2014}
\begin{equation}
\label{eq:binnedMu}
\bar{\mu}(z) = (1 - \alpha) \mu_b + \alpha \mu_{b+1},
\end{equation}
where they have defined 
$\alpha = \log\left(\frac{z}{z_b}\right)/\log\left(\frac{z_{b+1}}{z_b}\right)$ 
and $\mu_i$ is the distance modulus at control point $z_i$. 
Therefore, the data and covariance matrix are merely given at the 
31 control points log-spaced in the redshift range $0.01 < z < 1.3$.

>>>>

\section{Type \rom{1}a Supernovae}
\label{sec:SNIa}
\TM{TODO: Complete this section.}
\EW{You guys might want to read this over and tell me if you think I should
  change/add anything.}
A type \rom{1}a supernova (\sna{}) is a supernova with very little hydrogen or
helium absorption. It is believed that the progenitor for these special
supernovae are white dwarfs that are part of a binary system. These white
dwarfs accrete mass from their companion stars or merge with a companion white
dwarf or neutron star, causing them to exceed the Chandrasekhar limit
($1.44 M_\odot$). When this happens, carbon and oxygen fusion begins in the
core, and the temperature increases. However, the white dwarf does not expand
and cool as a main sequence star would, since it is supported by degeneracy
pressure rather than thermal, so the core experiences a runaway fusion
reaction, releasing $\sim 10^{44}$ J of energy
\citep[see, e.g.,][chap. 18.4]{ryden2010}, which is enough to overcome the
gravitational energy and the star explodes. Because all \snea{} are caused by a
similar reaction, they all have similar luminosities, and more importantly, the
light curves all have the same shape: a sharp maximum followed by a smooth,
gradual decay. Studying nearby \snea{} has shown that the rate of decline of
the light curve is correlated to the peak luminosity, and this correlation has
been calibrated using Cephied variable stars located in the same galaxies as
nearby \sna{}. With this information, we can estimate peak luminosity of an
\sna{} from its light curve, thereby providing us with a standard candle with
which to measure distance. They were first used in this way by the
Cal\'{a}n/Tololo Supernova Survey, and it was using \snea{} that
\citet{riess1998} and \citet{perlmutter1999} were able to discover the
accelerating expansion rate of the Universe for which three of the authors
later won the Nobel Prize in physics.

@@

\citet{betoule2014} define their ``joint light-curve analysis'' (JLA) 
sample, a total of 740 \snea{} compiled from a combination of data from the Sloan Digital Sky 
Survey (SDSS), the Supernova Legacy Survey (SNLS), the Hubble Space 
Telescope (HST), and several other experiments. The 613 SDSS \snea{} 
come from the SDSS supernova survey (SDSS-SNS) of SDSS-II \citep{sako2014} 
with redshifts of $0.05 < z < 0.4$, and 374 of them are selected from those 
that were confirmed in the spectroscopic follow-up. The rest of the 
\sne{} come from the compilation by \citet{conley2011}, which includes 
242 spectroscopically confirmed \snea{} from SNLS at redshifts $0.2 < z < 1$, 
14 \snea{} from HST at very high redshifts of $0.7 < z < 1.4$, and 123 
low redshift ($z < 0.08$) from a variety of sources. We made use of the 
publicly available distance moduli, redshifts, and covariance 
matrix provided by \citet{betoule2014}\footnote{Data is available 
for download via \url{http://cdsweb.u-strasbrg.fr/cgi-bin/qcat?J/A+A/568/A22}}. 
We note that the distance moduli are binned, so that they are only computed and 
given on a grid of redshifts. The distance modulus can then be well 
approximated by a piecewise linear function of $\log(z)$ that is given 
in a single redshift bin $z_b \le z < z_{b+1}$ as 
\citep[see][Appendix E.1]{betoule2014}
\begin{equation}
\label{eq:binnedMu}
\bar{\mu}(z) = (1 - \alpha) \mu_b + \alpha \mu_{b+1},
\end{equation}
where they have defined 
$\alpha = \log\left(\frac{z}{z_b}\right)/\log\left(\frac{z_{b+1}}{z_b}\right)$ 
and $\mu_i$ is the distance modulus at control point $z_i$. 
Therefore, the data and covariance matrix are merely given at the 
31 control points log-spaced in the redshift range $0.01 < z < 1.3$.
